%%
%% getstart.tex -- Flight Gear documentation: The FlightGear Manual
%% Chapter file
%%
%% Written by Michael Basler % Bernhard Buckel, starting September 1998.
%%
%% Copyright (C) 2002 Michael Basler
%%                  & Bernhard Buckel
%%
%% This program is free software; you can redistribute it and/or
%% modify it under the terms of the GNU General Public License as
%% published by the Free Software Foundation; either version 2 of the
%% License, or (at your option) any later version.
%%
%% This program is distributed in the hope that it will be useful, but
%% WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
%% General Public License for more details.
%%
%% You should have received a copy of the GNU General Public License
%% along with this program; if not, write to the Free Software
%% Foundation, Inc., 675 Mass Ave, Cambridge, MA 02139, USA.
%%
%% $Id: missed.tex,v 0.6 2002/09/09 michael
%% (Log is kept at end of this file)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifchinese
\chapter{{\\}复飞：如果有什么拒绝工作}
\fi
\iffalse
\IfLanguageName{english}{
\chapter{Missed approach: If anything refuses to work}
}{}
\IfLanguageName{french}{
\chapter{Approche manqu\'{e}e : si rien ne fonctionne}
}{}
\fi
\label{missed}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifchinese
\markboth{\thechapter.\hspace*{1mm} 复\space\space飞}{\thesection\hspace*{1mm} ???}
\fi
\iffalse
\IfLanguageName{english}{
\markboth{\thechapter.\hspace*{1mm} MISSED APPROACH}{\thesection\hspace*{1mm} ???}
}{}
\IfLanguageName{french}{
\markboth{\thechapter.\hspace*{1mm} APPROCHE MANQUEE}{\thesection\hspace*{1mm} ???}
}{}
\fi

\ifchinese
下面的章节，我们尝试按操作系统列出一些\Index{问题}，若你碰到一个问题，也许最好先看看“你的”操作系统。万一，如果你正在遇到问题，我们强烈建议你首先看看由 Cameron Moore\index{Moore Cameron} 维护的一份 \Index{FAQ}
\fi
\iffalse
\IfLanguageName{english}{
In the following section, we tried to sort some \Index{problems} according to operating system,
but if you encounter a problem, it may be a wise idea to look beyond ``your'' operating system -- just in case. If you are experiencing problems, we would strongly advise you to first check the \Index{FAQ} maintained by Cameron Moore\index{Moore Cameron} at
}{}
\IfLanguageName{french}{
Dans la section suivante, nous avons essay\'{e} de trier quelques \Index{probl\`{e}mes} qui peuvent \^{e}tre rencontr\'{e}s, en fonction des syst\`{e}mes d'exploitation. Cependant, si jamais vous rencontrez un probl\`{e}me, sachez qu'il peut parfois \^{e}tre une bonne id\'{e}e de regarder plus loin que ``votre'' syst\`{e}me d'exploitation - au cas o\`{u}. Si vous rencontrez des difficult\'{e}s, nous vous recommandons vivement de consulter en premier lieu la \Index{FAQ} maintenue par Cameron Moore\index{Moore Cameron} \`{a} l'adresse suivante :
}{}
\fi

\medskip

\web{http://wiki.flightgear.org/Frequently\_asked\_questions}.
\medskip

\ifchinese
另外，源码目录里的 \texttt{docs-mini} 目录也包含大量特定问题的解决方案。这里也可以找到更多参考。
\fi
\iffalse
\IfLanguageName{english}{
Moreover, the source code contains a directory \texttt{docs-mini} containing numerous
ideas on and solutions to special problems. This is also a good place to go for further reading.
}{}
\IfLanguageName{french}{
De plus, le code source comporte un r\'{e}pertoire \texttt{docs-mini} qui contient de nombreuses id\'{e}es
et solutions pour des probl\`{e}mes sp\'{e}cifiques. Il s'agit donc \'{e}galement d'un bon endroit pour trouver d'avantage d'informations.
}{}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifchinese
\section{FlightGear 问题报告}\index{problem report}
\fi
\iffalse
\IfLanguageName{english}{
\section{FlightGear Problem Reports}\index{problem report}
}{}
\IfLanguageName{french}{
\section{Signaler des probl\`{e}mes relatifs \`{a} FlightGear}\index{signaler un probl\`{e}me}
}{}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifchinese
寻找帮助最好的地方是\Index{邮件列表}，特别是 \textbf{[Flightgear-User]} 邮件列表。如果你恰好正在运行 Git 版本的 \FlightGear{}，你可以将问题报告给 \textbf{[Flightgear-Devel]} 相应的介绍可以看
\fi
\iffalse
\IfLanguageName{english}{
The best place to look for help is generally the \Index{mailing lists}, specifically the  \textbf{[Flightgear-User]} mailing list. If you happen to be running a Git version of \FlightGear{}, you may want to subscribe to the \textbf{[Flightgear-Devel]} list. Instructions for subscription can be found at
}{}
\IfLanguageName{french}{
Le meilleur endroit pour obtenir de l'aide est g\'{e}n\'{e}ralement de faire appel aux \Index{listes de diffusion}, et tout particuli\`{e}rement \`{a} la liste de diffusion \textbf{[Flightgear-User]}, ainsi que les \Index{forums}. Si jamais vous utilisez une version Git de \FlightGear{}, vous pourriez vouloir vous inscrire \`{a} la liste de diffusion \textbf{[Flightgear-Devel]}. Les informations pour s'y inscrire peuvent \^{e}tre trouv\'{e}es \`{a} l'adresse :
}{}
\fi

 \medskip
\web{http://www.flightgear.org/mail.html}.
 \medskip

\ifchinese
很多时候，也许别人已经解决了你遇到的问题，所以可以先在邮件列表存档里搜索一下
\fi
\iffalse
\noindent
\IfLanguageName{english}{
It's often the case that someone has already dealt with the issue you're dealing with, so it may be worth your time to search the mailing list archives at
}{}
\IfLanguageName{french}{
Bien souvent, vous n'\^{e}tes pas le premier \`{a} rencontrer ce type de difficult\'{e}. Donc une recherche sur les archives des listes de diffusion devrait vous permettre de trouver une solution rapide. Ces archives peuvent \^{e}tre consult\'{e}es \`{a} l'adresse :
}{}
\fi

 \medskip

\web{http://sourceforge.net/mailarchive/forum.php?forum\_name=flightgear-users}

\web{http://sourceforge.net/mailarchive/forum.php?forum\_name=flightgear-devel}.
 \medskip

\noindent

\ifchinese
你也可以去 \Index{FlightGear 论坛}搜索获得一些信息，有关论坛的介绍和存档：
\fi
\iffalse
\IfLanguageName{english}{
You should also consider searching the \Index{FlightGear forums} for help, instructions and archives at
}{}
\IfLanguageName{french}{
Vous devriez \'{e}galement consid\'{e}rer visiter les \Index{forums FlightGear} pour rechercher de l'aide, des instructions et des archives \`{a} l'adresse :
}{}
\fi

 \medskip
\web{http://www.flightgear.org/forums}.
 \medskip

\ifchinese
大量的开发者和用户会阅读这些邮件列表和论坛，因此泛泛而谈的问题，比如类似 \textit{FlightGear 在我的系统上不能编译，请问怎么做？} 这种没有提供更多信息的问题，很难获得回答。那么该如何做呢？当你报告问题的时候，可以加上这样一些信息：
\fi
\iffalse
\IfLanguageName{english}{
There are numerous developers and users reading those lists and forums, so questions are generally answered. However, messages of the type
\textit{FlightGear does not compile on my system. What shall I do?}
 \noindent
are hard to answer without any further detail given, aren't they? Here are some things to consider including in your message when you report a problem:
}{}
\IfLanguageName{french}{
De nombreux d\'{e}veloppeurs et utilisateurs lisent ces listes et forums, donc les questions trouvent g\'{e}n\'{e}ralement une r\'{e}ponse. Cependant, avouez qu'il est difficile de r\'{e}pondre \`{a} des messages du type :
\textit{Je n'arrive pas \`{a} compiler FlightGear sur mon syst\`{e}me, que dois-je faire ?}
 \noindent
si vous ne donnez pas plus de d\'{e}tails, non ? Voici donc quelques \'{e}l\'{e}ments qu'il serait bon d'inclure dans votre message lorsque vous signalez un probl\`{e}me :
}{}
\fi

 \medskip

\begin{itemize}
\ifchinese
\item \textbf{操作系统：}（Linux Fedora 17\ldots/Windows 7 64 位\ldots）
\item \textbf{计算机：} （奔腾酷睿双核 2.3GHz\ldots）
\item \textbf{显卡/芯片：} （ATI Radeon HD 770 XT/NVidia GeForce GTX 590\ldots）
\item \textbf{编译器/版本：}（GCC 版本 4.6.3\ldots）
\item \textbf{相关库的版本：}（PLIB 1.8.5, OpenSceneGraph 3.0.1\ldots）
\item \textbf{问题类型：}（链接器输出这些错误信息\ldots）
\item \textbf{复现问题的步骤：}（启动到 KSFO，关闭刹车\ldots）
\fi
\iffalse
\IfLanguageName{english}{
\item \textbf{Operating system:} (Linux Fedora 17\ldots/Windows Seven 64 bits\ldots)
\item \textbf{Computer:} (Pentium Dual Core, 2,3GHz\ldots)
\item \textbf{Graphics board/chip:} (ATI Radeon HD 770 XT/NVidia GeForce GTX 590\ldots)
\item \textbf{Compiler/version:} (GCC version 4.6.3\ldots)
\item \textbf{Versions of relevant libraries:} (PLIB 1.8.5, OpenSceneGraph 3.0.1\ldots)
\item \textbf{Type of problem:} (Linker dies with message\ldots)
\item \textbf{Steps to recreate the problem:} Start at KSFO, turn off brakes \ldots
}{}
\IfLanguageName{french}{
\item \textbf{Syst\`{e}me d'exploitation :} (Linux Fedora 17\ldots/Windows Seven 64 bits\ldots)
\item \textbf{Ordinateur :} (Pentium Dual Core, 2,3 GHz\ldots)
\item \textbf{Carte graphique/processeur :} (ATI Radeon HD 770 XT/Nvidia GeForce GTX 590\ldots)
\item \textbf{Compilateur/version :} (GCC version 4.6.3\ldots)
\item \textbf{Versions des librairies concern\'{e}es :} (PLIB 1.8.5, OpenSceneGraph 3.0.1\ldots)
\item \textbf{Type de probl\`{e}me :} (Le compilateur s'arr\^{e} avec le message suivant\ldots)
\item \textbf{Etapes pour reproduire le probl\`{e}me :} D\'{e}marrer \`{a} KSFO, l\^{a}cher les freins\ldots
}{}
\fi
\end{itemize}

\ifchinese
要想获得 \FlightGear{} 的追踪信息，以下命令也许会帮到你（可能需要针对操作系统做一些修改，也许其他系统不能工作）：
\fi
\iffalse
\IfLanguageName{english}{
For getting a trace of the output which \FlightGear{} produces, the following command may come in handy (may need to be modified on some OSs or may not work on others at all, though):
}{}
\IfLanguageName{french}{
Afin d'obtenir une trace de la sortie que \FlightGear{} produit, la commande suivante peut s'av\'{e}rer utile (elle devra \'{e}ventuellement \^{e}tre adapt\'{e}e sur certains syst\`{e}mes d'exploitation ou peut ne pas fonctionner du tout sur d'autres, d'ailleurs) :
}{}
\fi

\medskip

\texttt{\%FG$\underline{~}$ROOT/BIN/fgfs >log.txt 2>\&1}
\medskip

\ifchinese
\textbf{最后要说：}请不要向邮件列表发送二进制文件！邮件列表订阅者都是分散的，有些用户的网络连接可能很慢。过大的信件可能会被邮件列表管理员退掉。谢谢合作。
\fi
\iffalse
\IfLanguageName{english}{
\textbf{One final remark:} Please avoid posting binaries to these lists or forums! List subscribers are widely distributed, and some users have low bandwidth and/or metered connections. Large messages may be rejected by the mailing list administrator. Thanks.
}{}
\IfLanguageName{french}{
\textbf{Une derni\`{e}re petite remarque :} Merci d'essayer d'\'{e}viter de poster du code binaire sur ces forums ou sur ces listes ! Il y a de nombreux abonn\'{e}s et personnes consultant ces informations, et certains disposent de bandes passantes limit\'{e}es et/ou factur\'{e}es. Des messages trop volumineux pourraient \^{e}tre refus\'{e}s par l'administrateur des listes de diffusion. Merci.
}{}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifchinese
\section{通用问题}\index{问题!通用}
\fi
\iffalse
\IfLanguageName{english}{
\section{General problems}\index{problems!general}
}{}
\IfLanguageName{french}{
\section{Probl\`{e}mes g\'{e}n\'{e}raux}\index{probl\`{e}mes!g\'{e}n\'{e}raux}
}{}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\ifchinese
\item{\FlightGear{} 运行太太太慢了。}\\
如果 \FlightGear{} 运行时的帧速率只有 1 fps 或者低于普遍的情况，像是硬件不支持\Index{OpenGL}。也许有很多种原因。首先，也许老旧显卡不支持 OpenGL。如果是这样，建议换一块新显卡。

第二，检查驱动是不是安装正确。很多显卡除了 Windows “自带”的驱动还需要额外的 OpenGL 驱动支持。

\item{\texttt{configure} 或 \texttt{make} 命令卡在了找不到 \PLIB{} 头文件或库文件}\\
确保你已经编译并安装了最新版的 \PLIB{}（$>$ 1.8.4 版）。其头文件 \texttt{pu.h} 必须放在 \texttt{/usr/include/plib} 目录及其库里，比如 \texttt{libplibpu.a} 需要在 \texttt{/lib} 目录下。反复检查 \PLIB{} 的头文件和库文件是不是放在别的地方。

仔细检查 \texttt{configure} 命令输出的错误信息，很多情况下它会告诉你缺少了什么。
\fi
\iffalse
\IfLanguageName{english}{
\item{\FlightGear{} runs SOOO slow.}\\
 If \FlightGear{} says it's running with something like 1 fps
 (frame per second) or below you typically don't have working hardware
 \Index{OpenGL} support. There may be several reasons for this. First,
 there may be no OpenGL hardware drivers available for older
 cards. In this case it is highly recommended to get a new board.

 Second, check if your drivers are properly installed. Several
 cards need additional OpenGL support drivers besides the
 ``native'' windows ones.

\item{Either \texttt{configure} or \texttt{make} dies with not found \PLIB{} headers or
 libraries.}\\
  Make sure you have the latest version of \PLIB{} ($>$ version 1.8.4) compiled and installed.
  Its headers like \texttt{pu.h} have to be under \texttt{/usr/include/plib} and its libraries, like \texttt{libplibpu.a} should be under \texttt{/lib}. Double check there are no stray \PLIB{} headers/libraries sitting elsewhere!

  Besides, check carefully the error messages of \texttt{configure}. In several cases, it
  says what is missing.
}{}
\IfLanguageName{french}{
\item{\FlightGear{} fonctionne siiiiiii lentement.}\\
 Si \FlightGear{} fonctionne, disons \`{a} quelque chose comme une image par seconde
 (\textit{fps, frame per second}), ou moins, c'est que vous n'avez pas de mat\'{e}riel prenant en charge
 \Index{OpenGL}. Il peut y avoir plusieurs raisons \`{a} cela. Tout d'abord, il peut effectivement n'y avoir
 aucun pilote mat\'{e}riel OpenGL disponible pour des cartes anciennes. Dans ce cas, il vous est vivement
 recommand\'{e} d'envisager l'achat d'une nouvelle carte.

 Ensuite, v\'{e}rifiez que vos pilotes sont correctement install\'{e}s. Plusieurs cartes n\'{e}cessites des pilotes
 compl\'{e}mentaires pour faire fonctionner OpenGL en compl\'{e}ment des pilotes ``natifs'' du gestionnaire de fen\^{e}tres.

\item{\texttt{configure} ou \texttt{make} \'{e}chouent car ils ne trouvent pas les en-t\^{e}tes ou biblioth\`{e}ques \PLIB{}.}\\
  Soyez certains de disposer de la derni\`{e}re version de \PLIB{} ($>$ version 1.8.4) compil\'{e}e et install\'{e}e.
  Ses en-t\^{e}tes comme \texttt{pu.h} doivent se situer dans le r\'{e}pertoire \texttt{/usr/include/plib} et ses biblioth\`{e}ques,
  comme\texttt{libplibpu.a}, dans le r\'{e}pertoire \texttt{/lib}. V\'{e}rifiez \`{a} nouveaux qu'il n'y a pas d'autre en-t\^{e}tes ou biblioth\`{e}ques \PLIB{} parasites pr\'{e}sentes ailleurs !

  Enfin, v\'{e}rifiez attentivement les messages d'erreur(s) de \texttt{configure}. Dans de nombreux cas, ils donnent des informations pr\'{e}cieuses sur les \'{e}l\'{e}ments manquants.
}{}
\fi
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifchinese
\section{Linux 的潜在问题}\index{问题!Linux}
\fi
\iffalse
\IfLanguageName{english}{
\section{Potential problems under Linux}\index{problems!Linux}
}{}
\IfLanguageName{french}{
\section{Probl\`{e}mes potentiels sous Linux}\index{probl\`{e}mes!Linux}
}{}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifchinese
因为我们不能在所有 Linux 发行版下面测试问题，下面这些是可能出现的问题（此节感谢 Kai Troester 的贡献）。\index{Troester, Kai}
\fi
\iffalse
\IfLanguageName{english}{
Since we don't have access to all possible flavors of Linux distributions, here are some
thoughts on possible causes of problems. (This Section includes contributions by Kai
Troester.)\index{Troester, Kai}
}{}
\IfLanguageName{french}{
Comme nous n'avons pas acc\`{e}s \`{a} toutes les versions possibles des distributions Linux, voici quelques-
unes des causes possibles de probl\`{e}mes sous cet environnement. (Cette section comprend des contributions
de Kai Troester.)\index{Troester, Kai}
}{}
\fi

\begin{itemize}

\ifchinese
\item{错误的库版本}\\
这是手动安装 \FlightGear{} 时比较常碰上的问题。确认 Mesa 库已经包含了对 \Index{3DFX} 的支持，同时 \Index{GLIDE} 库已经安装并可以找到。如果 \texttt{ldd \` which fgfs\`} 命令告诉你有缺失的库，那就是遇到麻烦了。

你需要\emph{一直}确保 \PLIB{} 已经安装了\emph{最新版}。很多人编译 \FlightGear{} 失败大多是因为使用了过时的 plib。
\fi
\iffalse
\IfLanguageName{english}{
\item{Wrong library versions}\\
  This is a rather common cause of grief especially when you prefer to
  install the libraries needed by \FlightGear{} by hand. Be sure that
  especially the Mesa library contains support for the
  \Index{3DFX} board and that \Index{GLIDE} libraries are installed and can be
  found. If a \texttt{ldd \`which fgfs\`} complains about missing
  libraries you are in trouble.

  You should also be sure to \emph{always} keep the \emph{latest} version
  of \PLIB{} on your system. Lots of people have
  failed miserably to compile \FlightGear{} just because of an outdated
  plib.
}{}
\IfLanguageName{french}{
\item{Mauvaises versions des biblioth\`{e}ques}\\
  C'est une origine assez commune de griefs tout sp\'{e}cialement lorsque vous
  pr\'{e}f\'{e}rez installer les biblioth\`{e}ques n\'{e}cessaires \`{a} \FlightGear{}
  \`{a} la main. V\'{e}rifiez bien que, en particulier, la biblioth\`{e}que Mesa comprend bien
  la prise en charge de la carte \Index{3DFX} et que les biblioth\`{e}ques \Index{GLIDE} sont install\'{e}es et qu'elles peuvent \^{e}tre
  trouv\'{e}es. Si un \texttt{ldd \`which fgfs\`} se plaint de biblioth\`{e}ques manquantes, alors vous aurez des difficult\'{e}s.

  Soyez \'{e}galement certain de \emph{toujours} disposer de la \emph{derni\`{e}re} version
  de \PLIB{} sur votre syst\`{e}me. De nombreuses personnes ont lamentablement \'{e}chou\'{e} \`{a} compiler \FlightGear{} simplement
  \`{a} cause d'une version trop ancienne de plib.
}{}
\fi

\ifchinese
\item{缺少\Index{权限}}\\
如果你使用 4.0 发布版之前的 \Index{XFree86}，\FlightGear{} 的二进制文件可能需要 setuid 到 root 以获得访问某些基于 3DFX 图形加速卡的权限（或者如前文所述的特定内核模块）。
你可以用以下两种方法之一：

  \texttt{chown root.root /usr/local/bin/fgfs ;}\\
  \texttt{chmod 4755 /usr/local/bin/fgfs}

来给 \FlightGear{} 二进制文件赋予合适的权限或安装 3DFX 模块。后一种方法比较“干净”且强烈推荐！
\fi
\iffalse
\IfLanguageName{english}{
\item{Missing \Index{permissions}}\\
 In case you are using \Index{XFree86} before release 4.0 the \FlightGear{} binary may need to be  setuid root in order to be capable of  accessing some accelerator boards (or a special kernel module as described earlier in this document) based on 3DFX chips.
  So you can either issue a

  \texttt{chown root.root /usr/local/bin/fgfs ;}\\
  \texttt{chmod 4755 /usr/local/bin/fgfs}

  to give the \FlightGear{} binary the proper rights or install
  the 3DFX module. The latter is the ``clean''
  solution and strongly recommended!
}{}
\IfLanguageName{french}{
\item{Droits \Index{manquants}}\\
 Si vous utilisez \Index{XFree86} d'une version ant\'{e}rieure \`{a} 4.0, le binaire \FlightGear{} peut n\'{e}cessiter de disposer du bit setuid
 root afin de pouvoir acc\'{e}der \`{a} certaines cartes d'acc\'{e}l\'{e}ration (ou un module sp\'{e}cial du noyau comme d\'{e}crit pr\'{e}c\'{e}demment dans ce document) bas\'{e}es sur des puces 3DFX.
  Vous pouvez alors essayer un :

  \texttt{chown root.root /usr/local/bin/fgfs ;}\\
  \texttt{chmod 4755 /usr/local/bin/fgfs}

  pour donner au binaire \FlightGear{} les droits appropri\'{e}s ou installer le module 3DFX. Cette derni\`{e}re solution \'{e}tant la plus  ``propre'' et donc fortement recommand\'{e}e !
}{}
\fi

\ifchinese
\item{非默认安装选项}\\
\FlightGear{} 启动时会做大量的诊断。如果出现难看的界面或缺少文件，请检查是否按照预定的方法安装（最新的版本和适当的位置）。\FlightGear{} 需要其数据文件都在 \texttt{/usr/local/lib} 目录下。请确保已经获取所有最新版的组件！
\fi
\iffalse
\IfLanguageName{english}{
\item{Non-default install options}\\
  \FlightGear{} will display a lot of diagnostics while starting up.
  If it complains about bad looking or missing files, check that you
  installed them in the way they are supposed to be installed (i.e\. with the latest
  version and in the proper location). The canonical location \FlightGear{}
  wants its data files under \texttt{/usr/local/lib}.
  Be sure to grab the latest versions of everything that might be needed!
}{}
\IfLanguageName{french}{
\item{Options d'installation particuli\`{e}res}\\
  \FlightGear{} affichera un nombre important d'informations de diagnostic lors de son lancement.
  S'il se plaint de fichiers incorrects ou manquants, v\'{e}rifiez que vous les avez install\'{e}s de
  la mani\`{e}re dont ils sont suppos\'{e}s \^{e}tre install\'{e}s (c'est-\`{a}-dire dans leur version
  la plus r\'{e}cente et \`{a} l'emplacement pr\'{e}vu). L'emplacement canonique de \FlightGear{}
  attend ses donn\'{e}es dans le r\'{e}pertoire \texttt{/usr/local/lib}.
  Soyez certain de r\'{e}cup\'{e}rer les derni\`{e}res versions de tout ce qui peut \^{e}tre n\'{e}cessaire !
}{}
\fi

\ifchinese
\item{编译错误}\\
确保你安装了最新（官方）版的 gcc。旧版 gcc 会有大量的问题！另一方面，某些版本的 RedHat 7.0 编译 \FlightGear{} 时出现问题，因为使用了原始版本的 gcc。
\fi
\iffalse
\IfLanguageName{english}{
\item{Compile problems in general}\\
  Make sure you have the latest (official) version of gcc. Old versions of
  gcc are a frequent source of trouble! On the other hand, some versions
  of the RedHat 7.0 reportedly have certain problems compiling \FlightGear{} as they include
  a preliminary version of gcc.
}{}
\IfLanguageName{french}{
\item{Probl\`{e}mes plus g\'{e}n\'{e}raux de compilation}\\
  Soyez certain de disposer de la derni\`{e}re version officielle de gcc. D'anciennes version de gcc
  la cause de nombreux probl\`{e}mes ! D'un autre c\^{o}t\'{e}, certaines version de RedHat 7.0 sont connues pour avoir
  des difficult\'{e}s de compilation de \FlightGear{}, car elles incluent une version pr\'{e}liminaire de gcc.
}{}
\fi

 \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifchinese
\section{Windows 的潜在问题}\index{problems!Windows}
\fi
\iffalse
\IfLanguageName{english}{
\section{Potential problems under Windows}\index{problems!Windows}
}{}
\IfLanguageName{french}{
\section{Probl\`{e}mes potentiels sous Windows}\index{probl\`{e}mes!Windows}
}{}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\ifchinese
\item{可执行文件拒绝运行}\\
也许你需要直接在 Windows 资源管理器里双击 \texttt{fgfs.exe} 文件，或者通过 MS-DOS 命令行运行。如果在资源管理器里双击也不管用（除非你在 \texttt{autoexec.bat} 或其他地方修改了 \texttt{FG\_ROOT} 环境变量），可以双击 \texttt{fgrun}。更多相关信息可以参考第~\ref{takeoff} 章。

另一种导致这种问题的可能性是你没有下载新版的 \FlightGear{} 基础包，或者你根本没有下载。请仔细留意，因为地景/贴图格式还在开发中会经常变化。相关细节请参考第~\ref{prefligh} 章。

下一步，如果在运行时出现问题，不要使用 Windows 实用工具解压 \texttt{.tar.gz} 文件。如果需要解压，可以在 Cygnus shell 里执行 \texttt{tar xvfz} 命令。
\fi
\iffalse
\IfLanguageName{english}{
\item{The executable refuses to run.}\\
 You may have tried to start the executable directly either by
 double-clicking \texttt{fgfs.exe} in Windows Explorer or by invoking it
 within a MS-DOS shell. Double-clicking via Explorer never works
 (unless you set the environment variable \texttt{FG\_ROOT}
 in \texttt{autoexec.bat} or otherwise). Rather double-click \texttt{fgrun}.
  For more details, check Chapter~\ref{takeoff}.

 Another cause of grief might be that you did not download the
 most recent versions of the base package files required by \FlightGear{}, or
 you did not download any of them at all. Have a close look
 at this, as the scenery/texture format is still under development and may
 change frequently.  For more details, check Chapter~\ref{prefligh}.

 Next, if you run into trouble at runtime, do not use Windows utilities for unpacking the
 \texttt{.tar.gz}. If you did, try it in the Cygnus shell with \texttt{tar xvfz}
 instead.
}{}
\IfLanguageName{english}{
\item{L'ex\'{e}cutable refuse de se lancer.}\\
 Vous pouvez avoir essay\'{e} de lancer l'ex\'{e}cutable directement en double-cliquant sur \texttt{fgfs.exe}
 dans l'explorateur Windows ou en l'invoquant au travers d'une invite de commandes MS-DOS. Double-cliquer via
 l'explorateur de fonctionne jamais (sauf si vous avez d\'{e}fini la variable d'environnement \texttt{FG\_ROOT}
 dans l'\texttt{autoexec.bat} ou d'une autre mani\`{e}re). Pr\'{e}f\'{e}rez le double-clic sur \texttt{fgrun}.
 Pour plus de d\'{e}tails, consultez le chapitre~\ref{takeoff}.

 Une autre cause de grief peut s'expliquer par le fait que vous n'avez pas t\'{e}l\'{e}charg\'{e} les versions les
 plus r\'{e}centes du paquetage de base n\'{e}cessaires \`{a} \FlightGear{}, ou que vous ne les avez pas t\'{e}l\'{e}charg\'{e}
 du tout. Jetez souvent un \oe{}il \`{a} ceux-ci, car le format des sc\`{e}nes et des textures fait toujours l'objet d'un
 d\'{e}veloppement intensif. Pour plus de d\'{e}tails, reportez-vous au chapitre~\ref{prefligh}.

 Ensuite, si vous rencontrez un probl\`{e}me au d\'{e}marrage, n'utilisez pas les utilitaires Windows pour d\'{e}compresser
 les fichiers \texttt{.tar.gz}. Si vous l'avez fait, essayez de le faire dans l'invite de commandes Cygnus en pr\'{e}f\'{e}rant un \texttt{tar xvfz} \`{a} la place.
}{}
\fi
\ifchinese
\item{\FlightGear{} 忽略命令行参数}\\
可能是因为传递参数时包含了“=”字符，这样会创建批处理进程而不是响应命令行参数。
\fi
\iffalse
\IfLanguageName{english}{
\item{\FlightGear{} ignores the command line parameters.}\\
 There can be a problem with passing command line options containing a
 ''='' on the command line. Instead create a batch job to include your options and run that instead.
}{}
\IfLanguageName{french}{
\item{\FlightGear{} ignore les param\`{e}tres de ligne de commande.}\\
 Il peut y avoir une difficul\'{e} \`{a} passer des options de ligne de commande contenant un caract\`{e}re ''='' sur la ligne de commande. Pr\'{e}f\'{e}rez plut\^{o}t la cr\'{e}ation d'un fichier \textit{batch} pour y inclure vos options et lancez plut\^{o}t celui-ci.
}{}
\fi

\ifchinese
\item{我不能在 \Index{MSVC}/\Index{MS DevStudio} 下构建 \FlightGear{}}\\
默认情况下，\FlightGear{} 使用 GNU GCC 来构建。在 Win32 下移植的 GNU GCC 是 \Index{Cygwin}。有关 \textit{Makefiles} 对 MSVC 或 MSC DevStudio 的需求可以看：
\fi
\iffalse
\IfLanguageName{english}{
\item{I am unable to build \FlightGear{} under \Index{MSVC}/\Index{MS DevStudio}.}\\
 By default, \FlightGear{} is build with GNU GCC. The Win32 port of GNU GCC is known as
 \Index{Cygwin}. For hints on \textit{Makefiles} required for MSVC or MSC DevStudio have a look into
}{}
\IfLanguageName{french}{
\item{Je ne parviens pas \`{a} compiler \FlightGear{} avec \Index{MSVC}/\Index{MS DevStudio}.}\\
 Par d\'{e}faut, \FlightGear{} est compil\'{e} avec GNU GCC. Le portage Win32 de GNU GCC est connu sous le nom de
 \Index{Cygwin}. Pour obtenir des astuces sur les fichiers \textit{Makefile} n\'{e}cessaires pour MSVC ou MSC DevStudio veuillez consulter :
}{}
\fi

  \medskip

 \web{https://www.gitorious.org/fg/flightgear/trees/next}.
  \medskip

 \noindent
\ifchinese
原则上，可以使用源代码里的项目文件编译 \FlightGear{}。
\fi
\iffalse
\IfLanguageName{english}{
In principle, it should be possible to compile \FlightGear{} with the project files provided with the source code.
}{}
\IfLanguageName{french}{
En princpe, il devrait \^{e}tre possible de compiler \FlightGear{} \`{a} l'aide des fichiers de projet fournis avec le code source.
}{}
\fi

\ifchinese
\item{编译 \FlightGear{} 失败}\\
有很多原因导致，可能是 bug。然而在报告问题之前，确保已经使用了最新版的 \Cygwin{} 编译器。确保无虞，最好运行 \texttt{setup.exe} 并下载最新版的文件，因为这些文件可能经常变动。 
\fi
\iffalse
\IfLanguageName{english}{
\item{Compilation of \FlightGear{} dies.}\\
 There may be several reasons for this, including true bugs. However, before trying to do
 anything else or report a problem, make sure you have the latest version of the
 \Cygwin{} compiler. In case of doubt, start
 \texttt{setup.exe} anew and download and install the most recent versions of bundles
 as they possibly may have changed.
}{}
\IfLanguageName{french}{
\item{La compilation de \FlightGear{} \'{e}choue.}\\
 Il peut y avoir plusieurs raisons \`{a} cela, y compris l'existence de v\'{e}ritables anomalies. Cependant, avant
 de tenter quoi que ce soit ou de signaler un probl\`{e}me, soyez certain de disposer de la derni\`{e}re version du compilateur
 \Cygwin{}. En cas de doute, lancez \`{a} nouveau \texttt{setup.exe} et t\'{e}l\'{e}chargez et installez la version la plus r\'{e}cente
 de l'ensemble, car il est possible que cette version ait chang\'{e}.
}{}
\fi

\end{itemize}


%% revision 0.10  1998/10/01  bernhard
%% added win stuff michael
%% final proofreading for release
%% revision 0.11  1998/11/01  michael
%% Remark on mini-OpenGL drivers, new general Section
%% Access violation error under win32 added
%% Command line problem in win32 added
%% revision 0.12  1999/03/07  bernhard
%% Remark on EGCS compiler
%% revision 0.12  1999/03/07  michael
%% Added Contribution by Kai Troester
%% Reworked Win32 Stuff
%% revision 0.20  1999/06/04  michael
%% added hint to FAQ, gfc problem
%% revision 0.22 XXX
%% added hint on install.exe with Cygnus
%% revision 0.3 2000/04/20 michael
%% hint on revised PLIB paths, removed outdated stuff
%% revision 0.3 2000/04/20 michael
%% Deleted some outdated stuff
%% Added Old PLIB problem
%% revision 0.31 2000/05/01 michael
%% Reworked/Added Achnowledgements
%% Added hint on gunzip/tar from Marc Anderson
%% revision 0.4 2001/05/12 michael
%% added some points (RedHat...), deleted some outdated ones
%% complete rewrite and check still to be done ... sometime
%% revision 0.5 2002/01/01 michael
%% removed several outdated issues
%% Added problem linking MetaKit
%% revision 0.601 2002/09/14 michael
%% activated two links
